A simplified dynamic bioenergetic model for coral-algal symbiosis and coral bleaching

### 2016-10-28 JTB_supp/JTB_supp.Rmd
update sigmaC*

* $\sigma_{NH}, \sigma_{CH}, \sigma_{NS}, \sigma_{CS}$: Proportions of nitrogen and carbon recycled from host and symbiont biomass turnover

@@

>>>>

* $\sigma_{NH}, \sigma_{NS}$: Proportions of nitrogen recycled from host and symbiont biomass turnover

@@

* $\sigma_{CH},  \sigma_{CS}$: Proportions of CO~2~ recycled to photosynthesis from host and symbiont biomass turnover
    + Assuming that metabolic CO~2~ rapidly converts to HCO~3~^-^ at intracellular pH ~ 7.2 [@Venn:2009hy], only ~10% actually remains as CO~2~ [@Zeebe:2001wz] which would be available to diffusively supply photosynthesis. This passive supply is differentiated from all active mechanisms (CCMs) that facilitate CO~2~ supply to photosynthesis, which are separately treated collectively as the $jCO~2~$ flux.
    + Values used: 0.10
